### 2012-06-20 inst/examples/Reed.Rmd
Reed with uniform large noise
Reed with uniform large noise, logistic map

``` {r }
#f <- function(x,h,p){
#	S = x - h
#	p[1] * S * (1 - S/p[2]) + S
#}
````

@@

``` {r }
#pars <- c(r, K)
````

## OR

We consider a Beverton Holt state equation governing population dynamics, \\( f(x,h) = \frac{A x}{1 + B x} \\)

``` {r }
f <- BevHolt
````

With parameters `A` = `r A <- 1.5` and `B` = `r B <- 0.05`.

``` {r }
pars <- c(1.5, 0.05)
K <- (pars[1] - 1)/pars[2]
````

@@

``` {r miscpars}
delta <- 0.05
xT <- 0
OptTime <- 25
sigma_g <- .1
````

@@

``` {r  p0}
ggplot(subset(dt,reps==1)) +
  geom_line(aes(time, fishstock)) +
  geom_abline(intercept=opt$S, slope = 0) +
  geom_line(aes(time, harvest), col="darkgreen") 
````

@@

``` {r  p1}
p1 <- ggplot(dt) + geom_abline(intercept=opt$S, slope = 0) + 
  geom_abline(intercept=xT, slope = 0, lty=2) 
p1 + geom_line(aes(time, fishstock, group = reps), alpha = 0.2)
````

>>>>

``` {r }
f <- function(x,h,p){
	S = x - h
	p[1] * S * (1 - S/p[2]) + S
}
````

@@

``` {r }
pars <- c(r, K)
````

@@

``` {r miscpars}
delta <- 0.05
xT <- 0
OptTime <- 25
sigma_g <- .5
````

@@

``` {r  p0}
p0 <- ggplot(subset(dt,reps==1)) +
  geom_line(aes(time, fishstock)) +
  geom_abline(intercept=opt$S, slope = 0) +
  geom_line(aes(time, harvest), col="darkgreen") 
p0
````

@@

``` {r  p1}
p1 <- ggplot(dt) + geom_abline(intercept=opt$S, slope = 0) + 
  geom_abline(intercept=xT, slope = 0, lty=2) 
p1 <- p1 + geom_line(aes(time, fishstock, group = reps), alpha = 0.2)
p1
````
